Modeling Intervention Strategies for United States TB Control

### 2014-03-02 in_progress/presentations/paper/draft.tex
notation edits

{\huge \color{red} List of results}
Plan:
\begin{enumerate}
  \item Intervention Analysis: 
    \begin{enumerate}
      \item Reducing Entering LTBI
      \item Cutting Transmission
      \item Reducing Progression Rate
    \end{enumerate}
  \item Qualitative Strategy Conclusions:
    \begin{enumerate}
      \item Sourced Incidence \& Cost
      \item Plateauing Effect
      \item Extremal values for entering LTBI reduction
      \item Linearity in Cost/Incidence for entering LTBI reduction
      \item CPCA data
    \end{enumerate}
  \item Statistical Verification/Agent Based Feasibility
    \begin{enumerate}
      \item Normal Distributions
      \item Basic Reproductive Numbers
      \item Agetn based running time \& Extensibility. 
    \end{enumerate}
\end{enumerate}
Ideas:
\begin{itemize}
  \item Plateauing Effect
  \item Intervention Analysis
  \item Statistical Analysis of Hill Model
  \item Agent-Based Feasibility
  \item Theoretical/Experimental justification of basic reproduction number
  \item Overall qualitative strategy conclusions. 
\end{itemize}

@@

\section{Background}
\subsection{Tuberculosis}
Tuberculosis is an infectious bacterial disease that primarily affects the lungs,
with common symptoms including severe coughing, fevers, and chest pain.
Tuberculosis is a major global health concern, the World Health Organization
 estimates that 8.6 million developed TB and and 1.3 million people died from
 the disease in 2012.  As an airborne disease, \emph{Mycobacterium tuberculosis}
 is typically transmitted from person-to-person by coughing, sneezing, and the 
exchange of other respiratory fluids.  Infected individuals first enter a latent phase,
 during which \emph{Mycobacterium tuberculosis} is present in their bodies,
but the individuals remain asymptomatic and noncontagious. 
The lifetime risk of progressing from Latent TB Infection (LTBI) to Active TB is approximately
5-10\%, although individuals with LTBI have the greatest chance of developing 
Active TB during the first two years immediately following infection. 
Cases of Active TB may be classified as pulmonary (~80\% of cases) or 
non-pulmonary (~20\% of cases), depending upon the biological location of infection.
In the Hill model, pulmonary Active TB is treated as contagious and non-pulmonary 
Active TB is treated as  non-contagious, which is an assumption we also use here.  \\

>>>>

{\huge \color{red} List of results}
Plan:
\begin{enumerate}
  \item Intervention Analysis: 
    \begin{enumerate}
      \item Reducing Entering LTBI
      \item Cutting Transmission
      \item Reducing Progression Rate
    \end{enumerate}
  \item Qualitative Strategy Conclusions:
    \begin{enumerate}
      \item Sourced Incidence \& Cost
      \item Plateauing Effect
      \item Extremal values for entering LTBI reduction
      \item Linearity in Cost/Incidence for entering LTBI reduction
      \item CPCA data
    \end{enumerate}
  \item Statistical Verification/Agent Based Feasibility
    \begin{enumerate}
      \item Normal Distributions
      \item Basic Reproductive Numbers
      \item Agent based running time \& Extendibility. 
    \end{enumerate}
\end{enumerate}
Ideas:
\begin{itemize}
  \item Plateauing Effect
  \item Intervention Analysis
  \item Statistical Analysis of Hill Model
  \item Agent-Based Feasibility
  \item Theoretical/Experimental justification of basic reproduction number
  \item Overall qualitative strategy conclusions. 
\end{itemize}

@@

\section{Background}
\subsection{Tuberculosis}
Tuberculosis is an infectious bacterial disease that primarily affects the lungs,
with common symptoms including severe coughing, fevers, and chest pain.
Tuberculosis is a major global health concern, the World Health Organization
 estimates that 8.6 million developed TB and and 1.3 million people died from
 the disease in 2012.  As an airborne disease, \emph{Mycobacterium tuberculosis}
 is typically transmitted from person-to-person by coughing, sneezing, and the 
exchange of other respiratory fluids.  Infected individuals first enter a latent phase,
 during which \emph{Mycobacterium tuberculosis} is present in their bodies,
but the individuals remain asymptomatic and noncontagious. 
The lifetime risk of progressing from Latent TB Infection (LTBI) to Active TB is approximately
5-10\%, although individuals with LTBI have the greatest chance of developing 
Active TB during the first two years immediately following infection. 
Cases of Active TB may be classified as pulmonary ($\sim$80\% of cases) or 
non-pulmonary ($\sim$20\% of cases), depending upon the biological location of infection.
In the Hill model, pulmonary Active TB is treated as contagious and non-pulmonary 
Active TB is treated as  non-contagious, which is an assumption we also use here.  \\
